Measurement and Probability in Fuzzy Quantum Theories

### 2016-11-27 proposal/prop.tex
From: Sabry, Amr A. Sent: Sunday, November 27, 2016 16:08 To: Tai, Yu-Tsung <yuttai@indiana.edu> Cc: Sabry, Amr A. <sabry@indiana.edu>; Hanson, Andrew J. <hansona@indiana.edu>; Ortiz, Gerardo <ortizg@indiana.edu> Subject: Re: a section on Hough and Bayes and computable numbers
I didn’t like the sigma_0^{N-1}. It made many of the formulae difficult to read. I changed all of them to sigma_1^N but perhaps I missed some. Fix them if you have time. Thanks! —Amr

> On Nov 27, 2016, at 4:03 PM, Tai, Yu-Tsung <yuttai@indiana.edu> wrote:
>
> This is a rather small thing... I noticed that some array are

As motivated above, an event $E_{1}$ may have an interval of
probability $[l_{1},r_{1}]$. Assume that another disjoint event
$E_{2}$ has an interval of probability $[l_{2},r_{2}]$, what is the
interval of probability for the event $E_{1}\cup E_{2}$? The answer is
somewhat subtle: although it is possible to use the sum of the
intervals $[l_{1}+l_{2},r_{1}+r_{2}]$ as the combined probability, one
can find a much tighter interval if information \emph{against} the
event (i.e., information about the complement event) is also taken
into consideration. Formally, for a general event $E$ with probability
$[l,r]$, the evidence that contradicts $E$ is evidence supporting the
complement of $E$.  The complement of $E$ must therefore have
probability $\left[1-r,1-l\right]$ which we abbreviate
$\left[1,1\right]-\left[l,r\right]$.  Given a sample space~$\Omega$
and its set of events~$\events$, a
function~$\bar{\mu}:\events\rightarrow[0,1]$ is a classical
interval-valued probability measure if and only if $\bar{\mu}$
satisfies the following conditions~\cite{JamisonLodwick2004} where the
last line uses $\subseteq$ to allow for tighter intervals that exploit
the complement event:
\begin{itemize}
\item $\bar{\mu}(\emptyset)=[0,0]$.
\item $\bar{\mu}(\Omega)=[1,1]$. 
\item For any event $E$,
  $\bar{\mu}\left(\Omega\backslash E\right)=\left[1,1\right]-\bar{\mu}\left(E\right)$
\item For a collection $\left\{ E_{i}\right\} _{i=0}^{N}$ of pairwise
  disjoint events, we have
  $\bar{\mu}\left(\bigcup_{i=0}^{N}E_{i}\right)\subseteq\sum_{i=0}^{N}\bar{\mu}\left(E_{i}\right)$.
\end{itemize}

>>>>

As motivated above, an event $E_{1}$ may have an interval of
probability $[l_{1},r_{1}]$. Assume that another disjoint event
$E_{2}$ has an interval of probability $[l_{2},r_{2}]$, what is the
interval of probability for the event $E_{1}\cup E_{2}$? The answer is
somewhat subtle: although it is possible to use the sum of the
intervals $[l_{1}+l_{2},r_{1}+r_{2}]$ as the combined probability, one
can find a much tighter interval if information \emph{against} the
event (i.e., information about the complement event) is also taken
into consideration. Formally, for a general event $E$ with probability
$[l,r]$, the evidence that contradicts $E$ is evidence supporting the
complement of $E$.  The complement of $E$ must therefore have
probability $\left[1-r,1-l\right]$ which we abbreviate
$\left[1,1\right]-\left[l,r\right]$.  Given a sample space~$\Omega$
and its set of events~$\events$, a
function~$\bar{\mu}:\events\rightarrow[0,1]$ is a classical
interval-valued probability measure if and only if $\bar{\mu}$
satisfies the following conditions~\cite{JamisonLodwick2004} where the
last line uses $\subseteq$ to allow for tighter intervals that exploit
the complement event:
\begin{itemize}
\item $\bar{\mu}(\emptyset)=[0,0]$.
\item $\bar{\mu}(\Omega)=[1,1]$. 
\item For any event $E$,
  $\bar{\mu}\left(\Omega\backslash E\right)=\left[1,1\right]-\bar{\mu}\left(E\right)$
\item For a collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise
  disjoint events, we have
  $\bar{\mu}\left(\bigcup_{i=1}^{N}E_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(E_{i}\right)$.
\end{itemize}
